%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
   My objective is to obtain full-time employment in a rewarding atmosphere that makes use of my
   notable skills.

   As a programmer over the years, I have built many projects from the ground up and have extensive
   experience leading among my peers. I also have a history of good productivity and generally I have
   been known to be knowledgable in my field.

   In creating my organisation and building my Other Skies app, I learned a number of different skills
   in systems administration and development operations out of necessity. I built computers both for
   personal use, and to be used as server systems with remote access and full-stack hosting capabilities.
   I also learned to use many AWS, GitLab, and container system features to facilitate hosting this
   application.

   As an apprentice, I worked with individuals in construction and maintenance and learned to build
   and maintain different parts of a home. Building a deck is an experience I will forever hold as
   a fond memory and a constructive experience because it taught me how to properly use various power
   tools. As someone who does not get out much, of course the skills have come in handy.

   I enjoy contributing to open source projects and I love to build. Overall, I believe creativity
   and empathy are what sets me apart from the average individual and yet also enable me to work
   with many disparate groups. I love to learn new things and the pursuit of understanding is a folly
   with which I am greatly familiar and fully embrace.
\end{cvparagraph}
